Naturalness in U(1) extensions of the MSSM

### 2014-12-17 paper/e6ssm-tuning-paper.tex
added values of d coefficient.

In the MSSM the tuning can also be attcked more directly by looking at
chargino mass limikts as this rasies $\mu$ directly.  [Stuff aboiut
  chargino limits stiuts, then show plots in MSSM and E6SSM]
%    - plots of chargino bound impacts

The exact level of tuning from the $Z^\prime$ depends on the charges of
the extra $U(1)$ gauge symmetry it is associated with.  In Fig \ref{}
we look at the fine tuning for other U(1) extensions for the same
$Z^\prime$ masses as we did for the E$_6$SSM.
 % - if room, plots for different U(1)' charge Here we see that the As
can be seen in Fig.~\ref{} the severity of the tunings varies quite a
bit.  This is because the charges appear as coefficients in front of
the $Z^\prime$ mass in the EWSB condition.  These cagres change the
value of the coefficient $d$ in Eq.~\ref{}.  The values of the
coefficient $d$ in each model is [insert], and this determines which
of the models are most tuned.

@@

Finally we want to emphasise that while in Fig.~\ref{} the E$_6$SSM
looks more fine tuned than the MSSM this is depends on the cutoff
scale.  Indeed in \cite{} a constrained version of the E$_6$SSM, with
the cuttoff at the GUT scale, is considered and there the cE$_6$SSM
was found to be less tuned than the cMSSM. Since a 125 GeV Higgs can
be achieved in the E$_6$SSM with ligher stops, then if the cutoff is
large, the larger stop masses can make that model more
fine tuned due to large RGE effects.

As is shown in Fig.~\cite{} the tuning in the MSSM becomes larger
than that of the E$_6$SSM when the cuttoff scale is ?

>>>>

In the MSSM the tuning can also be attcked more directly by looking at
chargino mass limikts as this rasies $\mu$ directly.  [Stuff about
  chargino limits, then show plots in MSSM and E6SSM]
%    - plots of chargino bound impacts

The exact level of tuning from the $Z^\prime$ depends on the charges of
the extra $U(1)$ gauge symmetry it is associated with.  In Fig \ref{}
we look at the fine tuning for other U(1) extensions for the same
$Z^\prime$ masses as we did for the E$_6$SSM.
 % - if room, plots for different U(1)' charge Here we see that the As
can be seen in Fig.~\ref{} the severity of the tunings varies quite a
bit.  This is because the charges appear as coefficients in front of
the $Z^\prime$ mass in the EWSB condition.  These charges change the
value of the coefficient $d$ in Eq.~\ref{}.  The values of the
coefficient $d$ in each model is $\{-0.01, 0.40, 0.50, 0.81 \}$ for
$\{U(1)_I, U(1)_N, U(1)_\psi, U(1)_\eta \}$ and this determines which
of the models are most tuned.

@@

Finally we want to emphasise that while in Fig.~\ref{Fig:e6ssmvsmssm}
the E$_6$SSM looks more fine tuned than the MSSM this is depends on
the cutoff scale.  Indeed in \cite{Athron:2013ipa} a constrained
version of the E$_6$SSM, with the cuttoff at the GUT scale, is
considered and there the cE$_6$SSM was found to be less tuned than the
cMSSM. Since a 125 GeV Higgs can be achieved in the E$_6$SSM with
ligher stops, then if the cutoff is large, the larger stop masses can
make that model more fine tuned due to large RGE effects.

As is shown in Fig.~\ref{} the tuning in the MSSM becomes larger
than that of the E$_6$SSM when the cuttoff scale is ?
